---
title: "Github for Collab"
output:
  html_document:
    keep_md: yes
---

#Stat Group Assignment 
#By Zach Lin, Jason Tram, Mey So

```{r, message=FALSE, warning=FALSE}
library(moderndive)
library(skimr)
library(GGally)
library(openintro)
library(broom) 
library(tidyverse)
library(alr4)
library(ggmosaic)
library(ggridges)
library(fivethirtyeight)
```

<<<<<<< HEAD

```{r}
san_andreas %>% 
  ggplot() +
  geom_bar(aes(x = worry_bigone, fill = region))
```

=======
##Is it rude to recline your seat while on the airplane?

In this investigation, we will be using the data from *flying* posted by the *fivethirtyeight* package. We are interested in what factor(s) affects people perception of rudeness on the plane. The response variable here is whether people think reclining seat on the plane is rude (recline_rude) and the explanatory variables we are considering are: people's height and how frequently they themselves decline the seat (recline_frequency). 

(@) 
```{r}
data("flying")

flying %>% 
ggplot()+
  geom_count(aes(x= height, y= recline_rude, color =height))+
  theme_minimal()
```

```{r}
flying %>% 
ggplot()+
  geom_count(aes(x= recline_frequency, y= recline_rude, color =recline_frequency))+
  theme_minimal()
```


```{r}
flying %>% 
ggplot()+
  geom_count(aes(x= height, y= recline_rude, color =recline_frequency))
```
=======
>>>>>>> 7b2c5d4a2daa48487ebacb235f08fba7e8ff1c2a
```

## San Andreas Fault

>>>>>>> 4e1ba15d0146ce6049ffdd7b24890ffd8dcca33e
```{r}
san_andreas %>% 
  ggplot() +
  geom_jitter(aes(x = age, y = experience, color = prepared))
```

```{r}
san_andreas %>% 
  ggplot() +
<<<<<<< HEAD
  geom_bar(aes(x = fam_san_andreas, fill = worry_bigone))
```

=======
  geom_jitter(aes(x = age, y = experience, color = prepared))
```

```{r}
san_andreas %>% 
  ggplot() +
  geom_bar(aes(x = fam_san_andreas, fill = worry_bigone))
```

## Hate Crimes

```{r}
hc<-hate_crimes[-c(9),] #observation 9 (DC) produced to much interference when combined with other data states. Also doesn't count as a state, so thought it would be best to remove it's data from data wrangling 

hc
```
```{r} 
hc %>% 
  ggplot(aes(x=median_house_inc, y=hate_crimes_per_100k_splc))+ #Southern Poverty Law Center
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
hc %>% 
  ggplot(aes(x=gini_index, y=hate_crimes_per_100k_splc))+ #Southern Poverty Law Center
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
```
```{r}
hc %>% 
  ggplot(aes(x = share_non_white, y = hate_crimes_per_100k_splc))+
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
hc %>% 
  ggplot(aes(x = share_white_poverty, y = hate_crimes_per_100k_splc))+
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
hc %>% 
  ggplot(aes(x = share_unemp_seas, y = hate_crimes_per_100k_splc))+
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
```







>>>>>>> 4e1ba15d0146ce6049ffdd7b24890ffd8dcca33e

