---
title: "Github for Collab"
output:
  html_document:
    keep_md: yes
---

#Stat Group Assignment 
#By Zach Lin, Jason Tram, Mey So

```{r, message=FALSE, warning=FALSE}
library(moderndive)
library(skimr)
library(GGally)
library(openintro)
library(broom) 
library(tidyverse)
library(alr4)
library(ggridges)
library(fivethirtyeight)
```

#Is it rude to recline your seat while on the airplane?

In this investigation, we will be using the data from *flying* posted by the *fivethirtyeight* package. We are interested in what factor(s) affects people perception of rudeness on the plane. The response variable here is whether people think reclining seat on the plane is rude (recline_rude) and the explanatory variables we are considering are: people's height and how frequently they themselves decline the seat (recline_frequency). 

(@) 
```{r}
data("flying")

flying %>% 
ggplot()+
  geom_count(aes(x= height, y= recline_rude, color =height))+
  theme_minimal()
```

```{r}
flying %>% 
ggplot()+
  geom_count(aes(x= recline_frequency, y= recline_rude, color =recline_frequency))+
  theme_minimal()
```


```{r}
flying %>% 
ggplot()+
  geom_count(aes(x= height, y= recline_rude, color =recline_frequency))
```
```

