---
title: "Final Project"
author: "Zachary Lim"
output:
  html_document:
---

```{r, message=FALSE, warning=FALSE}
library(moderndive)
library(skimr)
library(GGally)
library(openintro)
library(broom) 
library(tidyverse)
library(alr4)
library(ggmosaic)
library(ggridges)
library(fivethirtyeight)
```

## Hate Crimes

```{r}
hc<-hate_crimes[-c(9),] #observation 9 (DC) produced to much interference when combined with other data states. Also doesn't count as a state, so thought it would be best to remove it's data from data wrangling 

hc
```
```{r} 
hc %>% 
  ggplot(aes(x=median_house_inc, y=hate_crimes_per_100k_splc))+ #Southern Poverty Law Center
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
hc %>% 
  ggplot(aes(x=gini_index, y=hate_crimes_per_100k_splc))+ #Southern Poverty Law Center
  geom_text(aes(label=state_abbrev),
            alpha=0.7,size=2.5) +
  geom_smooth(se = FALSE, method = "lm")
```


What to include: 

(@) Describe the data and your research question. Where does it come from? How was it collected? What do you hope to learn?

(@) 2-4 graphs with explanations about what the graphs show.

(@) At least 2 models. Explain why you chose to fit these models and interpret the coefficients of the model. What do they mean in the context of your research question? 

(@) Make some inferences, using either hypothesis testing or confidence intervals. What did you learn?

(@) Discuss next steps.

